Performing Cluster Analysis on TAD boundaries & Annotations

### 2019-03-24 Scripts/evaluating_pca.Rmd
saving plots

## Saving plots clustered annotation plots

@@

  data <- data.frame(data)

  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/cluster_by_tad/", 
                       cl, resolution, predictortype, annotation,
                       ".png", sep=""),
      width=11, height=8, units="in", res = 300)
  print({
    autoplot(prcomp(data[,-c(dim(data)[2]-1,dim(data)[2])]),
             data=data,
             #loadings = TRUE,
             label = FALSE, 
             #label.size = 3,
             #label.repel=T, 
             colour="Cluster",
             #shape="Medoid",
             size=3,
             frame = TRUE, 
             frame.type = 'norm',
             label.show.legend = FALSE) +
      theme_bw()
  })
  dev.off()

@@

>>>>

## Saving clustered annotation plots

@@

  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/cluster_by_tad/", 
                       cl, resolution, predictortype, cluster,
                       ".png", sep=""),
      width=11, height=8, units="in", res = 300)
  print({
    autoplot(prcomp(data[,-c(dim(data)[2]-1,dim(data)[2])]),
             data=data,
             #loadings = TRUE,
             label = FALSE, 
             #label.size = 3,
             #label.repel=T, 
             colour="Cluster",
             #shape="Medoid",
             #size=3,
             #frame = TRUE, 
             #frame.type = 'norm',
             label.show.legend = FALSE) +
      theme_bw()
  })
  dev.off()

@@

### Saving clustered tad plots

####GM12878

```{r}
tadclusterplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "count", cluster = "kmedoids")
tadclusterplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "count", cluster = "kmeans")

tadclusterplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "perc", cluster = "kmedoids")
tadclusterplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "perc", cluster = "kmeans")

tadclusterplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "dist", cluster = "kmedoids")
tadclusterplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "dist", cluster = "kmeans")

tadclusterplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "count", cluster = "kmedoids")
tadclusterplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "count", cluster = "kmeans")

tadclusterplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "perc", cluster = "kmedoids")
tadclusterplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "perc", cluster = "kmeans")

tadclusterplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "dist", cluster = "kmedoids")
tadclusterplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "dist", cluster = "kmeans")

tadclusterplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "count", cluster = "kmedoids")
tadclusterplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "count", cluster = "kmeans")

tadclusterplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "perc", cluster = "kmedoids")
tadclusterplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "perc", cluster = "kmeans")

tadclusterplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "dist", cluster = "kmedoids")
tadclusterplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "dist", cluster = "kmeans")

tadclusterplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "count", cluster = "kmedoids")
tadclusterplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "count", cluster = "kmeans")

tadclusterplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "perc", cluster = "kmedoids")
tadclusterplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "perc", cluster = "kmeans")

tadclusterplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "dist", cluster = "kmedoids")
tadclusterplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "dist", cluster = "kmeans")

#### K562

```{r}
tadclusterplotfunction(cl = "K562", resolution = "10kb", predictortype = "count", cluster = "kmedoids")
tadclusterplotfunction(cl = "K562", resolution = "10kb", predictortype = "count", cluster = "kmeans")

tadclusterplotfunction(cl = "K562", resolution = "10kb", predictortype = "perc", cluster = "kmedoids")
tadclusterplotfunction(cl = "K562", resolution = "10kb", predictortype = "perc", cluster = "kmeans")

tadclusterplotfunction(cl = "K562", resolution = "10kb", predictortype = "dist", cluster = "kmedoids")
tadclusterplotfunction(cl = "K562", resolution = "10kb", predictortype = "dist", cluster = "kmeans")

tadclusterplotfunction(cl = "K562", resolution = "25kb", predictortype = "count", cluster = "kmedoids")
tadclusterplotfunction(cl = "K562", resolution = "25kb", predictortype = "count", cluster = "kmeans")

tadclusterplotfunction(cl = "K562", resolution = "25kb", predictortype = "perc", cluster = "kmedoids")
tadclusterplotfunction(cl = "K562", resolution = "25kb", predictortype = "perc", cluster = "kmeans")

tadclusterplotfunction(cl = "K562", resolution = "25kb", predictortype = "dist", cluster = "kmedoids")
tadclusterplotfunction(cl = "K562", resolution = "25kb", predictortype = "dist", cluster = "kmeans")

tadclusterplotfunction(cl = "K562", resolution = "50kb", predictortype = "count", cluster = "kmedoids")
tadclusterplotfunction(cl = "K562", resolution = "50kb", predictortype = "count", cluster = "kmeans")

tadclusterplotfunction(cl = "K562", resolution = "50kb", predictortype = "perc", cluster = "kmedoids")
tadclusterplotfunction(cl = "K562", resolution = "50kb", predictortype = "perc", cluster = "kmeans")

tadclusterplotfunction(cl = "K562", resolution = "50kb", predictortype = "dist", cluster = "kmedoids")
tadclusterplotfunction(cl = "K562", resolution = "50kb", predictortype = "dist", cluster = "kmeans")

tadclusterplotfunction(cl = "K562", resolution = "100kb", predictortype = "count", cluster = "kmedoids")
tadclusterplotfunction(cl = "K562", resolution = "100kb", predictortype = "count", cluster = "kmeans")

tadclusterplotfunction(cl = "K562", resolution = "100kb", predictortype = "perc", cluster = "kmedoids")
tadclusterplotfunction(cl = "K562", resolution = "100kb", predictortype = "perc", cluster = "kmeans")

tadclusterplotfunction(cl = "K562", resolution = "100kb", predictortype = "dist", cluster = "kmedoids")
tadclusterplotfunction(cl = "K562", resolution = "100kb", predictortype = "dist", cluster = "kmeans")
